Draft Exploration

### 2020-04-14 draft_exploration.Rmd
added redraft prob explanation to shiny

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(ggthemes)
library(ggplot2)
library(janitor)
library(dplyr)
library(gt)
library(readxl)
library(sf)
library(scales)
library(magrittr)
library(haven)
library(infer)
library(Lahman)
library(xml2)
library(rvest)
library(DataCombine)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(ggthemes)
library(ggplot2)
library(janitor)
library(dplyr)
library(gt)
library(readxl)
library(sf)
library(scales)
library(magrittr)
library(haven)
library(infer)
library(Lahman)
library(xml2)
library(rvest)
library(DataCombine)
library(RColorBrewer)
```
